Inferring neural networks from fluorescent calcium imaging using partial correlation and sample weighting

### 2014-06-06 article.tex
add comment

Since only observational data are available, the network recovery is set as an
unsupervised learning problem. Whenever a partial knowledge of the target
network or known networks highly similar to the unknown one is available,
supervised learning [todo cite] and transfer learning  [todo cite] based
approach could be considered to infer networks.

>>>>

\textcolor{red}{AJ: Should we keep the following paragraph? While interesting
                this might not be relevant for a 6 page abstract.}
Since only observational data are available, the network recovery is set as an
unsupervised learning problem. Whenever a partial knowledge of the target
network or known networks highly similar to the unknown one is available,
supervised learning [todo cite] and transfer learning  [todo cite] based
approach could be considered to infer networks.
